Relationships in the extremes and their influence on competition and coexistence

### 2021-07-08 paper/Paper.Rnw
workingon intro

While there are multiple studies on the influence of extremes (due to climate change), the influence of relationships in their extremes (also due to climate change), has not yet been explored. The lottery model within the framework of coexistence theory provides a suitable opportunity to explore extreme relationships and the consequences to coexistence.

%Jasmin, I think the below makes a pretty good start at tryinbg to nail down a good way to express our goals
%in the last para of the Intro, so please incorporate these into your last para. If you have a better way
%to phrase these, please put both so we can compare at some point when we meet.
G1) To augment the modern theory of coexistence (MTC) to show how asymmetric tail association (ATA)
plays a role. The MTC decomposes a measure of coexistence into components due to each of several mechanisms. 
We address how ATA contributes to these components. We here examine mechanisms of coexistence that apply in 
models exhibiting solely temporal variation; spatial variation can be considered in future work.
G2) To explore, using a simple model, the relative magnitudes of the contributions to coexistence that come
from ATA compared to other mechanisms.

>>>>

paragraph to inuitively explain storage effects
We emphasize that although this paper focuses on storage effects, it is still a paper generally about the importance of asymmetrical tail associations for coexistence because we do consider whether they are important for other mechanisms of modern coexistence theory, though we quickly realize their importance is solely for storage effects

[As we know], anthropogenic climate change has large consequences for almost all aspects of life including via extreme climatic events, which have only become more extreme - increasing in magnitude and frequency - and have contributed to the increase in global means as well as an increase in environmental variability. While there are multiple studies on the influence of environmental extremes and varaibility on competition and coexistence (Parepa et al 2013, Diez et al 2012), the influence of relationships and interactions between drivers in their extremes, has not yet been explored. By definition, interacting environmental drivers that are  moreso related in the extreme values are tail associated, thus we have implemented our tools for the study of tail associations to explore the importance of environmental relationships in their exrtemes on competition and coexistence. Environmental variability has been classically shown to promote coexistence via storage mechanisms (Chesson and Warner 1981, Warner and Chesson 1985), hence we continue/move forward with this simple model to examine the effect of extreme relationships between environmental variables on the contribution of storage effects to coexistence.

The lottery model within the framework of coexistence theory provides a suitable opportunity to explore extreme relationships and the consequences to coexistence.

Results main ideas + example

introduce new decomposition

final parahraph:goals
%Jasmin, I think the below makes a pretty good start at tryinbg to nail down a good way to express our goals
%in the last para of the Intro, so please incorporate these into your last para. If you have a better way
%to phrase these, please put both so we can compare at some point when we meet.
G1) To augment the modern theory of coexistence (MTC) to show how asymmetric tail association (ATA)
plays a role. The MTC decomposes a measure of coexistence into components due to each of several mechanisms. 
We address how ATA contributes to these components. We here examine mechanisms of coexistence that apply in 
models exhibiting solely temporal variation; spatial variation can be considered in future work.
G2) To explore, using a simple model, the relative magnitudes of the contributions to coexistence that come
from ATA compared to other mechanisms.
